Bow shocks, bow waves, and dust waves

### 2018-05-24 papers/Papers1234/sec-dust-bow-intro.tex
Move the Cloudy dust models to an appendix

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
  \caption{Drag force as a function of gas--grain slip velocity,
    \(w\), for different values of the grain potential,
    \(\phi = U / k T\).  Contributions from proton and electron Coulomb
    (electrostatic) drag, as well as Epstein (solid-body) drag are
    indicated.  Inset shows \(\phi\) as a function of the radiation
    parameter, \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a
    log--linear scale.}
  \label{fig:gas-grain-drag-photoionized}
\end{figure*}

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/multi-dustprops}
  \caption{Dust properties as a function of radius from star for three
    selected Cloudy models. (a)~\SI{40}{M_\odot} main-sequence star in
    medium of density \SI{e4}{cm^{-2}}. (b)~\SI{10}{M_\odot} main-sequence
    star in medium of density \SI{1}{cm^{-2}}. (c)~Blue supergiant
    star in medium of density \SI{1}{cm^{-2}}}.
  \label{fig:multi-dustprops}
\end{figure*}

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/drift-pratio-4panel}
  \caption{Drift velocity versus radiation parameter \(\Xi_P\). Each line
    represents a model with ambient density and stellar type as
    indicated in the key.}
  \label{fig:drift-gn}
\end{figure*}

@@

The drag force on a charged dust grain moving at a relative speed
\(w\) through a plasma has contributions from both direct collisions
and from electrostatic Coulomb interactions with ions and electrons.
We use the expressions in \citet{Draine:1979a}, equations~(4)--(6),
summing over protons, electrons, and helium ions.\footnote{Helium is
  assumed to be 50\% neutral and 50\% singly ionized, leading to only
  a small contribution to the drag force.  For much hotter stars, such
  as the central stars of planetary nebulae, helium may be doubly
  ionized, which leads to a more significant drag contribution,
  especially around \(w \approx \SI{5}{km.s^{-1}}\).} %
Results are shown in Figure~\ref{fig:gas-grain-drag-photoionized} for
different values of \(\phi = e U / kT\), where \(U = e Z\grain / a \) is
the electrostatic potential of a grain of charge \(Z\grain\) and
radius \(a\).

>>>>

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/gas-grain-drag-photoionized}
  \caption{Dimensionless drag force, \(f\drag / f_*\), as a function
    of gas--grain slip velocity, \(w\), for different values of the
    grain potential in thermal units, \(\phi\).  Contributions from
    proton and electron Coulomb (electrostatic) drag, as well as
    Epstein (solid-body) drag are indicated.  Examples of subsonic and
    highly supersonic stable drift velocities are shown (thin dark
    blue arrows), where the drag force is in equilibrium with the
    radiation force (thick dark blue dashed lines), while blue shading
    indicates the unstable, mildly supersonic velocity regime, where
    no stable drift equilibrium exists.  Inset graph shows \(\phi\) as a
    function of the radiation parameter,
    \(\Xi = P_{\mathrm{rad}} / P_{\mathrm{gas}}\) on a log--linear scale
    for a collection of Cloudy models (see
    Appendix~\ref{sec:cloudy-models-dust}).}
  \label{fig:gas-grain-drag-photoionized}
\end{figure*}

@@

The drag force on a charged dust grain moving at a relative speed
\(w\) through a plasma has contributions from both direct collisions
and from electrostatic Coulomb interactions with ions and electrons.
We use the expressions in \citet{Draine:1979a}, equations~(4)--(6),
summing over protons, electrons, and helium ions.\footnote{Helium is
  assumed to be 50\% neutral and 50\% singly ionized, leading to only
  a small contribution to the drag force.  For much hotter stars, such
  as the central stars of planetary nebulae, helium may be doubly
  ionized, which leads to a more significant drag contribution,
  especially around \(w \approx \SI{5}{km.s^{-1}}\).} %
Results are shown in Figure~\ref{fig:gas-grain-drag-photoionized} for
different values of the dimensionless grain potential:
\(\phi = e^2 Z\grain / a kT\), which is the electrostatic potential
energy of a unit charge at the surface of a grain of charge
\(Z\grain\) and radius \(a\), in units of the characteristic thermal
energy of a gas particle. 
The drag force \(f\drag\) is put in
dimensionless units by dividing by a characteristic force:
\begin{equation}
  \label{eq:fstar}
  f_* = 2 n k T \cdot \pi a^2 \ , 
\end{equation}
which is approximately the gas pressure multiplied by the grain
geometric cross section.
